MaxEnt: What is it good for?

### 2015-06-19 ms.tex
sentence
New figure, tweaks

The principle may be used
to {\it assign} or {\it update} a
subjective\footnote{in the sense that the probability distribution is a model
of the state of uncertainty of an idealised rational agent, rather than
a {\it frequency distribution} such as a histogram of people's heights.}
probability distribution when you obtain a certain kind of information
called {\it testable information}. In this article I will focus on the
updating application, as the assigning application can be viewed as a special
case where the prior distribution happened to be
uniform\footnote{A uniform probability distribution, either over a discrete
hypothesis space, or a continuous one with respect to a continuous, may be
justified by a symmetry argument or simply asserted as in the
``subjective Bayesian'' approach.}.

@@

\section{Probability}
We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $\{A_1, A_2, ..., A_N\}$ which we will usually
think of as possible values of an unknown quantity $x$.
On the basis of background
information $I$ (hereafter suppressed), we know that one and only one of these
propositions is true (i.e. the true value of $x$ is in our set),
but we don't know which. We model states of
uncertainty by probability distributions over the hypothesis space,
such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
The standard loose Bayesian notation would write this distribution simply
as $p(x)$.

@@

>>>>

The principle may be used
to {\it assign} or {\it update} a
subjective\footnote{in the sense that the probability distribution is a model
of the state of uncertainty of an idealised rational agent, rather than
a {\it frequency distribution} such as a histogram of people's heights.}
probability distribution when you obtain a certain kind of information
called {\it testable information}. In this article I will focus on the
updating application, as the assigning application can be viewed as a special
case where the prior distribution happened to be
uniform\footnote{A uniform probability distribution, either over a discrete
hypothesis space, or a continuous one with respect to a specific choice of
parameterisation, may be justified by a symmetry argument, or simply asserted
as in the ``subjective Bayesian'' approach.}.

@@

\section{Probability}
We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $A_1$, $A_2$, ..., $A_N$ which we will usually
think of as possible values of an unknown quantity $x$. For example,
$A_1 \equiv $``$x=1$'', $A_2 \equiv $``$x=2$'', and so on.
On the basis of background
information $I$ (hereafter suppressed), we know that one and only one of these
propositions is true (i.e. the true value of $x$ is in our set),
but we don't know which. We model states of
uncertainty by probability distributions over the hypothesis space,
such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
The standard loose Bayesian notation would write this distribution simply
as $p(x)$.

@@

Clearly, the distribution $q(x)$ doesn't satisfy this constraint, so we
need to update to a new distribution $p(x)$ using MaxEnt.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{distribution2.pdf}
\caption{\label{fig:distribution2}}
\end{center}
\end{figure}
